---
title: "Igraph_R"
author: "Jieun Park"
date: "`r Sys.Date()`"
output: html_document
---

# Library

```{r}
library(igraph)
library(dplyr)
```

# Basic Igraph Package

## 1

```{r}
g <- graph( c(1,2, 2,3, 3,4, 3,5))
g
class(g)
is_igraph(g)
```

```{r}
g <- graph( c(1,2, 2,3, 3,4, 3,5),directed=F) # undirected graph
g
```

```{r}
E(g) # edge table
V(g) # node table
```

```{r}
E(g)$weight <- c(0.2,0.3,0.2,0.5) #the `weight` attribute is a reserved one
V(g)$name <- c("juan","lola","pepe","saul","ana") #the `name` attribute is a reserved one
V(g)$color <- c("red","blue","blue","red","blue")

g
```
Another way to make the graph data

```{r}
edges <- data.frame(from=c(1,1,2,2,3,5),to=c(2,3,3,4,2,4),peso=c(1,1,1,2,2,3))
nodes <- data.frame(id=c(1,2,3,4,5),nombre=c("juan","clara","luis","raul","alex"))
g <- graph.data.frame(edges,vertices=nodes)
g
```
Read / Write Graph

```{r}
# 1. Read
g <- read.graph(file, format = c("edgelist", "pajek", "ncol",
"lgl","graphml", "dimacs", "graphdb", "gml", "dl"), ...)

# 2. Write
write.graph(g,format="Pajek",file="g.net")
```


## 2. enron data

```{r}
library(igraphdata)
data(enron) #We load the enron emails graph
enron
```

## 3. Starwars data

```{r}
net <- jsonlite::fromJSON(txt="data/starwars-full-interactions-allCharacters-merged.json")
names(net)
```
```{r}
nodes <- net$nodes
links <- net$links

head(nodes,2) # name, value, colour
head(links,5) # source, target, value

# Remember that the first column in the table nodes must contain the same ids that the firs two columns in links. This is why we add a new column to this file.
# Same as the code below
# nodes <- data.frame(id=seq(0,nrow(nodes)-1),nodes)
nodes <- nodes %>%
  mutate(id = row_number() - 1, .before = 'name') # id should be located at the most first order


```

Generate the graph

```{r}
gSW <- graph_from_data_frame(links,vertices=nodes,directed=FALSE)
gSW
```

### example of graph_from_data_frame and vice versa as_data_frame (igraph)

```{r}

## A simple example with a couple of actors
## The typical case is that these tables are read in from files....
actors <- data.frame(
  name = c(
    "Alice", "Bob", "Cecil", "David",
    "Esmeralda"
  ),
  age = c(48, 33, 45, 34, 21),
  gender = c("F", "M", "F", "M", "F")
)
relations <- data.frame(
  from = c(
    "Bob", "Cecil", "Cecil", "David",
    "David", "Esmeralda"
  ),
  to = c("Alice", "Bob", "Alice", "Alice", "Bob", "Alice"),
  same.dept = c(FALSE, FALSE, TRUE, FALSE, FALSE, TRUE),
  friendship = c(4, 5, 5, 2, 1, 1), advice = c(4, 5, 5, 4, 2, 3)
)
g <- graph_from_data_frame(relations, directed = TRUE, vertices = actors)
print(g, e = TRUE, v = TRUE)

## The opposite operation
as_data_frame(g, what = "vertices")
as_data_frame(g, what = "edges")

```

Making a plot

```{r}
par(mar=c(0,0,0,0))
plot(gSW)
```
```{r}
head(V(gSW))
```

Vertex (edge) internal ids run from 1 to $|V|$ ($|E|$). Internal ids are used typically in functions. Original ids are stored in V(g)$name

```{r}
V(gSW)[1]
which(V(gSW)=="DARTH VADER")
which(V(gSW)$name=="DARTH VADER")
```

### Graph Operation: subsetting

Nodes that are neighbors of a

```{r}
head(V(gSW)[.nei("DARTH VADER")])
```

Edges between groups of nodes (direction matters):

Overall, the code snippet extracts the subset of edges from the graph gSW where the source nodes are "DARTH VADER" or "LUKE" and the target nodes are "R2-D2" or "C-3PO". It's essentially querying the graph for edges connecting these specific nodes.

```{r}
E(gSW)[c("DARTH VADER","LUKE") %->% c("R2-D2","C-3PO")]
```

### Igraph function for subsetting

Incident nodes are the nodes directly connected to a specified node through edges.

```{r}
head(neighbors(gSW,"DARTH VADER")) #get the int. ids of a node’s neighbor
head(incident(gSW,"DARTH VADER")) #get the incident edges to a node
```

### example of incident node

```{r}
g <- make_graph("Zachary")
incident(g, 1)
incident(g, 34)
```

### Graph operations: operations

### example of subgraph

```{r}
g <- make_ring(10)
g2 <- induced_subgraph(g, 1:7)
g3 <- subgraph.edges(g, 1:5)

g
g2
g3
```


We can modify the graph

Adding/deleting vertices/edges

```{r}
# Adding
gSW <- gSW + vertex("ANAKIN",color="blue")
gSW <- gSW + edge("DARTH VADER","ANAKIN")

# Deleting
gSW <- delete_vertices(gSW,"ANAKIN")
```

Simplify the graph: remove loops and multiple edges

```{r}
gSW <- simplify(gSW,remove.multiple = T,remove.loops = T)
```

Subgraphs: only specified vertices and edges between them are kept

<Parameter>
- vids : Numeric vector, the vertices of the original graph which will form the subgraph.

```{r}
gSW_subg <- induced_subgraph(gSW,vids = c("DARTH VADER","LUKE","PADME","LEIA"))
plot(gSW_subg)
```
We can also get only the neighborhood of a given node

<Parameter>
- order: Integer giving the order of the neighborhood.
The order of the ego network. An ego network of order 0 contains only the ego (the central node) itself. An ego network of order 1 contains the ego and all nodes directly connected to it. An ego network of order 2 contains the ego, all nodes directly connected to it, and all nodes that are one edge away from the ego, and so on.



```{r}
egoDW <- make_ego_graph(gSW,order = 1,"DARTH VADER")[[1]]
plot(egoDW)
```


















